#End of Section Quizzes 

## 1. Introduction to Loss Data Analytis

### Section 1.1 

```{r child = './Quizzes/Quiz11.html'}
```

### Section 1.2

```{r child = './Quizzes/Quiz12.html'}
```

### Section 1.3

```{r child = './Quizzes/Quiz13.html'}
```
## 2. Frequency Modeling

### Section 2.1

```{r child = './Quizzes/Quiz21.html'}
```

### Section 2.2

```{r child = './Quizzes/Quiz22.html'}
```

### Section 2.3

```{r child = './Quizzes/Quiz23.html'}
```

### Section 2.4


```{r child = './Quizzes/Quiz24.html'}
```

### Section 2.5

```{r child = './Quizzes/Quiz25.html'}
```

### Section 2.6

```{r child = './Quizzes/Quiz26.html'}
```

### Section 2.7

```{r child = './Quizzes/Quiz27.html'}
```

## 3. Modeling Loss Severity

### Section 3.1

```{r child = './Quizzes/Quiz31.html'}
```
### Section 3.2

```{r child = './Quizzes/Quiz32.html'}
```

### Section 3.3

```{r child = './Quizzes/Quiz33.html'}
```

### Section 3.4

```{r child = './Quizzes/Quiz34.html'}
```

### Section 3.5

```{r child = './Quizzes/Quiz35.html'}
```

## 4. Model Selection and Estimation

### Section 4.1

```{r child = './Quizzes/Quiz41.html'}
```

### Section 4.2

```{r child = './Quizzes/Quiz42.html'}
```

### Section 4.3

```{r child = './Quizzes/Quiz43.html'}
```

### Section 4.4

```{r child = './Quizzes/Quiz44.html'}
```
## 5. Aggregate Loss Models

### Section 5.1

```{r child = './Quizzes/Quiz51.html'}
```

### Section 5.2

```{r child = './Quizzes/Quiz52.html'}
```

### Section 5.3

```{r child = './Quizzes/Quiz53.html'}
```

### Section 5.4

```{r child = './Quizzes/Quiz54.html'}
```

### Section 5.5

```{r child = './Quizzes/Quiz55.html'}
```
## 8. Risk Classification

### Section 8.1

```{r child = './Quizzes/Quiz81.html'}
```

### Section 8.2

```{r child = './Quizzes/Quiz82.html'}
```

### Section 8.3

```{r child = './Quizzes/Quiz83.html'}
```
## 9. Experience Rating Using Credibility Theory

### Section 9.1

```{r child = './Quizzes/Quiz91.html'}
```

### Section 9.2

```{r child = './Quizzes/Quiz92.html'}
```

### Section 9.3

```{r child = './Quizzes/Quiz93.html'}
```

### Section 9.6


```{r child = './Quizzes/Quiz96.html'}
```

## 10. Insurance Portfolio Management including Reinsurance

### Section 10.1

```{r child = './Quizzes/Quiz101.html'}
```

### Section 10.2

```{r child = './Quizzes/Quiz102.html'}
```

### Section 10.3

```{r child = './Quizzes/Quiz103.html'}
```

## 13. Data and Systems

### Section 13.1


```{r child = './Quizzes/Quiz131.html'}
```

### Section 13.2


```{r child = './Quizzes/Quiz132.html'}
```

### Section 13.3


```{r child = './Quizzes/Quiz133.html'}
```

## 14. Dependence Modeling

### Section 14.1

```{r child = './Quizzes/Quiz141.html'}
```

### Section 14.2


```{r child = './Quizzes/Quiz142.html'}
```

### Section 14.3

```{r child = './Quizzes/Quiz143.html'}
```

### Section 14.5

```{r child = './Quizzes/Quiz145.html'}
```

### Section 14.6

```{r child = './Quizzes/Quiz146.html'}
```